### 2013-07-23 paper.tex
proved bubble thm

Given a sequence consisting of the letters $s$ and $t$ of length $n$, as well as a binary string of length $n$, one can construct such a diagram using an algorithm known as Libednisky's light leaves, as detailed in section \ref{sec:prelim_lightleave}.  Since two diagrams may be composed, we may construct a new map given two binary strings by composing the results of two applications of the light leaves.  We describe the relationship between the final result of such a composition and the two binary strings being composed.

@@

In this section we will show several results which show that the possible outputs of a map with base $\AA_n$ are extremely restricted.  We present them below, before providing proofs of each.
\begin{theorem}[Bubble Theorem]
	Consider a bubble in a full-diagram with base $\AA_n$.  The bubble holds exactly one caterpillar.
	\label{thm:bubble}
\end{theorem}
\begin{theorem}[Caterpillar Theorem]
	Any caterpillar in a full-diagram with base $\AA_n$ evaluates in the form $x^my^n\alpha_s$ if it is blue, or $x^my^n\alpha_t$ is red.
	\label{thm:caterpillar}
\end{theorem}
\begin{theorem}[Pasture Theorem]
	Consider a full-diagram with $N+1$ pastures (numbered $0$, $1$, \dots, $N$) with base $\AA_n$ and top $T$.  Suppose further that $N \ge 1$ (or equivalently, $T \neq \varnothing$).  Then:
	\begin{enumerate}[(i)]
		\ii Pastures $1$ through $N-1$ contain either nothing or a free component.
		\ii Pasture $N$ contains nothing if $T[N] \neq \AA_n[n]$, and contains a single caterpillar otherwise.
	\end{enumerate}
	\label{thm:pasture}
\end{theorem}

\subsection{Proof of the Bubble Theorem}

Consider a bubble $B$ and assume without loss of generality that it is blue.  First, we verify that $B$ is nonempty.  Take any pair of blue anchors on the boundary of $B$.  Then there must be a red point between these two anchors, and it follows that there exists a component of red color inside the bubble, and hence at least one caterpillar.

Now we verify that there is at most one caterpillar.  Clearly any caterpillars held in the bubble must be red.  Now assume on the contrary that there are at least two caterpillars.

TODO: Finish this.

@@

\subsection{Proof of the Pasture Theorem}
TODO

>>>>

Given a sequence consisting of the letters $s$ and $t$ of length $n$, as well as a binary string of length $n$, one can construct such a diagram using an algorithm known as Libedinsky's light leaves, as detailed in section \ref{sec:prelim_lightleave}.  Since two diagrams may be composed, we may construct a new map given two binary strings by composing the results of two applications of the light leaves.  We describe the relationship between the final result of such a composition and the two binary strings being composed.

@@

In this section we will show several results which show that the possible outputs of a map with base $\AA_n$ are extremely restricted.  We present them below, before providing proofs of each.
\begin{theorem}[Bubble Theorem]
	Consider a bubble in a full-diagram with base $\AA_n$.  The bubble holds exactly one caterpillar, whose color is opposite that of the bubble.
	\label{thm:bubble}
\end{theorem}
\begin{theorem}[Caterpillar Theorem]
	Any caterpillar in a full-diagram with base $\AA_n$ evaluates in the form $x^my^n\alpha_s$ if it is blue, or $x^my^n\alpha_t$ is red.
	\label{thm:caterpillar}
\end{theorem}
\begin{theorem}[Pasture Theorem]
	Consider a full-diagram with $N+1$ pastures (numbered $0$, $1$, \dots, $N$) with base $\AA_n$ and top $T$.  Suppose further that $N \ge 1$ (or equivalently, $T \neq \varnothing$).  Then:
	\begin{enumerate}[(i)]
		\ii Pastures $1$ through $N-1$ contain either nothing or a free component.
		\ii Pasture $N$ contains nothing if $T[N] \neq \AA_n[n]$, and contains a single caterpillar otherwise.
	\end{enumerate}
	\label{thm:pasture}
\end{theorem}

\subsection{Proof of the Bubble Theorem}
We begin with a proof of the bubble theorem, which is the crux result of the alternating case.  Indeed, both of the subsequent theorems are fairly straightforward consequences of this theorem.

It's interesting to note that the Bubble Theorem is intuitively very natural.  The main difficulty is finding a clean way to handle the special cases generated by the convoluted geometry.

\begin{proof}[Proof of Theorem \ref{thm:bubble}]
	Take a bubble $B$ and assume without loss of generality that it is blue.  It is easy to see, by considering two anchors on the boundary of blue, that there is some red anchor inside $B$.  This implies that $B$ has at least one red caterpillar.

	Next, it is easy to verify that all caterpillars held inside $B$ are red, otherwise this contradicts the construction of Libedinsky's light leaves.  Then let $S$ be the set of anchors contained on the boundary of any caterpillars held inside $B$ (in a sense, on the ``outermost'' level).

	Define a pair of red anchors $u, v \in S$ to be \emph{quasi-connected} if one can draw an arc from $u$ to $v$ contained entirely in one half-map which does not intersect any boundaries of $B$, and furthermore, there is no other pair of red anchors both between $u$ and $v$, inclusive, with this property.

	Now we claim that \textbf{any quasi-connected pair of red anchors is actually joined by a single arc}.  To prove this, take such a quasi-connected pair $u$ and $v$.  Now we'll focus only on the half-map in which the prescribed arc is drawn.  We thus may state that an arc \emph{shields} any anchors between its endpoints.

	\begin{figure}[ht]
		\centering
		\begin{asy}
			size(6cm);
			pen s = blue, t = red + dashed + 0.6;
			pen dot_s = blue, dot_t = red;
			for (int i=0; i<=8; i+=2) { dot( (i,0), dot_s ); }
			for (int i=1; i<=8; i+=2) { dot( (i,0), dot_t ); }
			draw((0,0)..(1,2)..(3,4)..(5,3)..(6,5)..(7,2)..(8,0), s);
			draw((1,0)..(3,2)..(5,0), t); // red covering arc
			draw((2,0)..(3,1)..(4,0), s); // blue covering arc again
			label("$u$", (3,0), dir(-90));
			label("$v$", (5,0), dir(-90));
		\end{asy}
		\hspace{2em}
		\begin{asy}
			size(6cm);
			pen s = blue, t = red + dashed + 0.6;
			pen dot_s = blue, dot_t = red;
			for (int i=0; i<=8; i+=2) { dot( (i,0), dot_s ); }
			for (int i=1; i<=8; i+=2) { dot( (i,0), dot_t ); }
			draw((0,0)..(1,2)..(3,4)..(5,3)..(6,5)..(7,2)..(8,0), s);
			draw((1,0)..(4,2)..(7,0), t); // red covering arc
			draw((2,0)..(4,1)..(6,0), s); // blue covering arc
			label("$u$", (3,0), dir(-90));
			label("$v$", (5,0), dir(-90));
		\end{asy}
		\caption{Proving the bubble theorem with quasi-connected vertices.}
		\label{fig:pf_bubble}
	\end{figure}
	Because the string is alternating, there exists a blue anchor between $u$ and $v$, say $x$.  Furthermore, there must be some blue arc (of $B$) shielding $u$ and $v$.  By the light-leave construction, there must be some red arc $A$ covering $x$.  If this arc joins $u$ and $v$, then we are done.  Otherwise, it must completely cover either $u$ or $v$ (by quasi-connectedness).  Now we have two cases,
	\begin{itemize}
		\ii If the arc covers exactly one of $u$ or $v$, say $u$, then there must be a blue arc shielding $u$ from $A$.  But then this contradicts the quasi-connectedness, because now it is not possible to join $u$ and $v$ by an arc on this half-map.  This case is illustrated by the left half of figure \ref{fig:pf_bubble}.
		\ii If the arc covers both $u$ and $v$, then there must be a blue arc which shields both $u$ and $v$, which is itself shielded by $A$.  Then we can repeat the same procedure with this new blue arc.  This case is illustrated by the left half of figure \ref{fig:pf_bubble}.
	\end{itemize}
	Therefore any pair of quasi-connected anchors must be connected by an arc.  However, it is evident that this implies there is a path of arcs joining any pair of red anchors.  Therefore all red anchors in $S$ must be connected.  So there is a single caterpillar, as desired.
\end{proof}

@@

\subsection{Proof of the Pasture Theorem}
